Performances Code

### 2019-02-05 Scripts/performances.rmd
editted script for results

all10kbresults$Performance <- c(round(rfperf_gm12878_10kb_none[9,2],2),
                                round(rfperf_gm12878_10kb_none[19,2],2),
                                round(rfperf_gm12878_10kb_none[16,2],2),
                                round(rfperf_gm12878_10kb_none[15,2],2),
                                round(rfperf_K562_10kb_none[9,2],2),
                                round(rfperf_K562_10kb_none[19,2],2),
                                round(rfperf_K562_10kb_none[16,2],2),
                                round(rfperf_K562_10kb_none[15,2],2),
                                round(rfperf_gm12878_10kb_rus[9,2],2),
                                round(rfperf_gm12878_10kb_rus[19,2],2),
                                round(rfperf_gm12878_10kb_rus[16,2],2),
                                round(rfperf_gm12878_10kb_rus[15,2],2),
                                round(rfperf_K562_10kb_rus[9,2],2),
                                round(rfperf_K562_10kb_rus[19,2],2),
                                round(rfperf_K562_10kb_rus[16,2],2),
                                round(rfperf_K562_10kb_rus[15,2],2),
                                round(rfperf_gm12878_10kb_ros[9,2],2),
                                round(rfperf_gm12878_10kb_ros[19,2],2),
                                round(rfperf_gm12878_10kb_ros[16,2],2),
                                round(rfperf_gm12878_10kb_ros[15,2],2),
                                round(rfperf_K562_10kb_ros[9,2],2),
                                round(rfperf_K562_10kb_ros[19,2],2),
                                round(rfperf_K562_10kb_ros[16,2],2),
                                round(rfperf_K562_10kb_ros[15,2],2),
                                round(rfperf_gm12878_10kb_smote[9,2],2),
                                round(rfperf_gm12878_10kb_smote[19,2],2),
                                round(rfperf_gm12878_10kb_smote[16,2],2),
                                round(rfperf_gm12878_10kb_smote[15,2],2),
                                round(rfperf_K562_10kb_smote[9,2],2),
                                round(rfperf_K562_10kb_smote[19,2],2),
                                round(rfperf_K562_10kb_smote[16,2],2),
                                round(rfperf_K562_10kb_smote[15,2],2),
                                round(rfperf_gm12878_10kb_rose[9,2],2),
                                round(rfperf_gm12878_10kb_rose[19,2],2),
                                round(rfperf_gm12878_10kb_rose[16,2],2),
                                round(rfperf_gm12878_10kb_rose[15,2],2),
                                round(rfperf_K562_10kb_rose[9,2],2),
                                round(rfperf_K562_10kb_rose[19,2],2),
                                round(rfperf_K562_10kb_rose[16,2],2),
                                round(rfperf_K562_10kb_rose[15,2],2))

@@

f1mcc10kbplot <- ggplot(all10kbresults[which(all10kbresults$Metric=="F1-Score" |
                                               all10kbresults$Metric=="MCC"),],
                       aes(x=Resampling, y=Performance, fill=Metric)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ CL) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

@@

all25kbresults$Performance <- c(round(rfperf_gm12878_25kb_none[9,2],2),
                                round(rfperf_gm12878_25kb_none[19,2],2),
                                round(rfperf_gm12878_25kb_none[16,2],2),
                                round(rfperf_gm12878_25kb_none[15,2],2),
                                round(rfperf_K562_25kb_none[9,2],2),
                                round(rfperf_K562_25kb_none[19,2],2),
                                round(rfperf_K562_25kb_none[16,2],2),
                                round(rfperf_K562_25kb_none[15,2],2),
                                round(rfperf_gm12878_25kb_rus[9,2],2),
                                round(rfperf_gm12878_25kb_rus[19,2],2),
                                round(rfperf_gm12878_25kb_rus[16,2],2),
                                round(rfperf_gm12878_25kb_rus[15,2],2),
                                round(rfperf_K562_25kb_rus[9,2],2),
                                round(rfperf_K562_25kb_rus[19,2],2),
                                round(rfperf_K562_25kb_rus[16,2],2),
                                round(rfperf_K562_25kb_rus[15,2],2),
                                round(rfperf_gm12878_25kb_ros[9,2],2),
                                round(rfperf_gm12878_25kb_ros[19,2],2),
                                round(rfperf_gm12878_25kb_ros[16,2],2),
                                round(rfperf_gm12878_25kb_ros[15,2],2),
                                round(rfperf_K562_25kb_ros[9,2],2),
                                round(rfperf_K562_25kb_ros[19,2],2),
                                round(rfperf_K562_25kb_ros[16,2],2),
                                round(rfperf_K562_25kb_ros[15,2],2),
                                round(rfperf_gm12878_25kb_smote[9,2],2),
                                round(rfperf_gm12878_25kb_smote[19,2],2),
                                round(rfperf_gm12878_25kb_smote[16,2],2),
                                round(rfperf_gm12878_25kb_smote[15,2],2),
                                round(rfperf_K562_25kb_smote[9,2],2),
                                round(rfperf_K562_25kb_smote[19,2],2),
                                round(rfperf_K562_25kb_smote[16,2],2),
                                round(rfperf_K562_25kb_smote[15,2],2),
                                round(rfperf_gm12878_25kb_rose[9,2],2),
                                round(rfperf_gm12878_25kb_rose[19,2],2),
                                round(rfperf_gm12878_25kb_rose[16,2],2),
                                round(rfperf_gm12878_25kb_rose[15,2],2),
                                round(rfperf_K562_25kb_rose[9,2],2),
                                round(rfperf_K562_25kb_rose[19,2],2),
                                round(rfperf_K562_25kb_rose[16,2],2),
                                round(rfperf_K562_25kb_rose[15,2],2))

@@

f1mcc25kbplot <- ggplot(all25kbresults[which(all25kbresults$Metric=="F1-Score" |
                                               all25kbresults$Metric=="MCC"),],
                       aes(x=Resampling, y=Performance, fill=Metric)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ CL) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

@@

all50kbresults$Performance <- c(round(rfperf_gm12878_50kb_none[9,2],2),
                                round(rfperf_gm12878_50kb_none[19,2],2),
                                round(rfperf_gm12878_50kb_none[16,2],2),
                                round(rfperf_gm12878_50kb_none[15,2],2),
                                round(rfperf_K562_50kb_none[9,2],2),
                                round(rfperf_K562_50kb_none[19,2],2),
                                round(rfperf_K562_50kb_none[16,2],2),
                                round(rfperf_K562_50kb_none[15,2],2),
                                round(rfperf_gm12878_50kb_rus[9,2],2),
                                round(rfperf_gm12878_50kb_rus[19,2],2),
                                round(rfperf_gm12878_50kb_rus[16,2],2),
                                round(rfperf_gm12878_50kb_rus[15,2],2),
                                round(rfperf_K562_50kb_rus[9,2],2),
                                round(rfperf_K562_50kb_rus[19,2],2),
                                round(rfperf_K562_50kb_rus[16,2],2),
                                round(rfperf_K562_50kb_rus[15,2],2),
                                round(rfperf_gm12878_50kb_ros[9,2],2),
                                round(rfperf_gm12878_50kb_ros[19,2],2),
                                round(rfperf_gm12878_50kb_ros[16,2],2),
                                round(rfperf_gm12878_50kb_ros[15,2],2),
                                round(rfperf_K562_50kb_ros[9,2],2),
                                round(rfperf_K562_50kb_ros[19,2],2),
                                round(rfperf_K562_50kb_ros[16,2],2),
                                round(rfperf_K562_50kb_ros[15,2],2),
                                round(rfperf_gm12878_50kb_smote[9,2],2),
                                round(rfperf_gm12878_50kb_smote[19,2],2),
                                round(rfperf_gm12878_50kb_smote[16,2],2),
                                round(rfperf_gm12878_50kb_smote[15,2],2),
                                round(rfperf_K562_50kb_smote[9,2],2),
                                round(rfperf_K562_50kb_smote[19,2],2),
                                round(rfperf_K562_50kb_smote[16,2],2),
                                round(rfperf_K562_50kb_smote[15,2],2),
                                round(rfperf_gm12878_50kb_rose[9,2],2),
                                round(rfperf_gm12878_50kb_rose[19,2],2),
                                round(rfperf_gm12878_50kb_rose[16,2],2),
                                round(rfperf_gm12878_50kb_rose[15,2],2),
                                round(rfperf_K562_50kb_rose[9,2],2),
                                round(rfperf_K562_50kb_rose[19,2],2),
                                round(rfperf_K562_50kb_rose[16,2],2),
                                round(rfperf_K562_50kb_rose[15,2],2))

@@

f1mcc50kbplot <- ggplot(all50kbresults[which(all50kbresults$Metric=="F1-Score" |
                                               all50kbresults$Metric=="MCC"),],
                       aes(x=Resampling, y=Performance, fill=Metric)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ CL) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

@@

all100kbresults$Performance <- c(round(rfperf_gm12878_100kb_none[9,2],2),
                                round(rfperf_gm12878_100kb_none[19,2],2),
                                round(rfperf_gm12878_100kb_none[16,2],2),
                                round(rfperf_gm12878_100kb_none[15,2],2),
                                round(rfperf_K562_100kb_none[9,2],2),
                                round(rfperf_K562_100kb_none[19,2],2),
                                round(rfperf_K562_100kb_none[16,2],2),
                                round(rfperf_K562_100kb_none[15,2],2),
                                round(rfperf_gm12878_100kb_rus[9,2],2),
                                round(rfperf_gm12878_100kb_rus[19,2],2),
                                round(rfperf_gm12878_100kb_rus[16,2],2),
                                round(rfperf_gm12878_100kb_rus[15,2],2),
                                round(rfperf_K562_100kb_rus[9,2],2),
                                round(rfperf_K562_100kb_rus[19,2],2),
                                round(rfperf_K562_100kb_rus[16,2],2),
                                round(rfperf_K562_100kb_rus[15,2],2),
                                round(rfperf_gm12878_100kb_ros[9,2],2),
                                round(rfperf_gm12878_100kb_ros[19,2],2),
                                round(rfperf_gm12878_100kb_ros[16,2],2),
                                round(rfperf_gm12878_100kb_ros[15,2],2),
                                round(rfperf_K562_100kb_ros[9,2],2),
                                round(rfperf_K562_100kb_ros[19,2],2),
                                round(rfperf_K562_100kb_ros[16,2],2),
                                round(rfperf_K562_100kb_ros[15,2],2),
                                round(rfperf_gm12878_100kb_smote[9,2],2),
                                round(rfperf_gm12878_100kb_smote[19,2],2),
                                round(rfperf_gm12878_100kb_smote[16,2],2),
                                round(rfperf_gm12878_100kb_smote[15,2],2),
                                round(rfperf_K562_100kb_smote[9,2],2),
                                round(rfperf_K562_100kb_smote[19,2],2),
                                round(rfperf_K562_100kb_smote[16,2],2),
                                round(rfperf_K562_100kb_smote[15,2],2),
                                round(rfperf_gm12878_100kb_rose[9,2],2),
                                round(rfperf_gm12878_100kb_rose[19,2],2),
                                round(rfperf_gm12878_100kb_rose[16,2],2),
                                round(rfperf_gm12878_100kb_rose[15,2],2),
                                round(rfperf_K562_100kb_rose[9,2],2),
                                round(rfperf_K562_100kb_rose[19,2],2),
                                round(rfperf_K562_100kb_rose[16,2],2),
                                round(rfperf_K562_100kb_rose[15,2],2))

@@

f1mcc100kbplot <- ggplot(all100kbresults[which(all100kbresults$Metric=="F1-Score" |
                                               all100kbresults$Metric=="MCC"),],
                       aes(x=Resampling, y=Performance, fill=Metric)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ CL) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

@@

#Tables model performances

@@

>>>>

all10kbresults$Performance <- c(round(rfperf_gm12878_10kb_none[9,2],2),
                                round(rfperf_gm12878_10kb_none[19,2],2),
                                round(rfperf_gm12878_10kb_none[16,2],2),
                                round(rfperf_gm12878_10kb_none[15,2],2),
                                round(rfperf_K562_10kb_none[9,2],2),
                                round(rfperf_K562_10kb_none[19,2],2),
                                round(rfperf_K562_10kb_none[16,2],2),
                                round(rfperf_K562_10kb_none[15,2],2),
                                round(mean(rfperf_gm12878_10kb_rus[9,]),2),
                                round(mean(rfperf_gm12878_10kb_rus[19,]),2),
                                round(mean(rfperf_gm12878_10kb_rus[16,]),2),
                                round(mean(rfperf_gm12878_10kb_rus[15,]),2),
                                round(mean(rfperf_K562_10kb_rus[9,]),2),
                                round(mean(rfperf_K562_10kb_rus[19,]),2),
                                round(mean(rfperf_K562_10kb_rus[16,]),2),
                                round(mean(rfperf_K562_10kb_rus[15,]),2),
                                round(mean(rfperf_gm12878_10kb_ros[9,]),2),
                                round(mean(rfperf_gm12878_10kb_ros[19,]),2),
                                round(mean(rfperf_gm12878_10kb_ros[16,]),2),
                                round(mean(rfperf_gm12878_10kb_ros[15,]),2),
                                round(mean(rfperf_K562_10kb_ros[9,]),2),
                                round(mean(rfperf_K562_10kb_ros[19,]),2),
                                round(mean(rfperf_K562_10kb_ros[16,]),2),
                                round(mean(rfperf_K562_10kb_ros[15,]),2),
                                round(mean(rfperf_gm12878_10kb_smote[9,]),2),
                                round(mean(rfperf_gm12878_10kb_smote[19,]),2),
                                round(mean(rfperf_gm12878_10kb_smote[16,]),2),
                                round(mean(rfperf_gm12878_10kb_smote[15,]),2),
                                round(mean(rfperf_K562_10kb_smote[9,]),2),
                                round(mean(rfperf_K562_10kb_smote[19,]),2),
                                round(mean(rfperf_K562_10kb_smote[16,]),2),
                                round(mean(rfperf_K562_10kb_smote[15,]),2),
                                round(mean(rfperf_gm12878_10kb_rose[9,]),2),
                                round(mean(rfperf_gm12878_10kb_rose[19,]),2),
                                round(mean(rfperf_gm12878_10kb_rose[16,]),2),
                                round(mean(rfperf_gm12878_10kb_rose[15,]),2),
                                round(mean(rfperf_K562_10kb_rose[9,]),2),
                                round(mean(rfperf_K562_10kb_rose[19,]),2),
                                round(mean(rfperf_K562_10kb_rose[16,]),2),
                                round(mean(rfperf_K562_10kb_rose[15,]),2))

@@

f1mcc10kbplot <- ggplot(all10kbresults[which(all10kbresults$Metric=="F1-Score" |
                                               all10kbresults$Metric=="MCC"),],
                       aes(x=Resampling, y=Performance, fill=CL)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Cell Line")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

@@

all25kbresults$Performance <- c(round(rfperf_gm12878_25kb_none[9,2],2),
                                round(rfperf_gm12878_25kb_none[19,2],2),
                                round(rfperf_gm12878_25kb_none[16,2],2),
                                round(rfperf_gm12878_25kb_none[15,2],2),
                                round(rfperf_K562_25kb_none[9,2],2),
                                round(rfperf_K562_25kb_none[19,2],2),
                                round(rfperf_K562_25kb_none[16,2],2),
                                round(rfperf_K562_25kb_none[15,2],2),
                                round(mean(rfperf_gm12878_25kb_rus[9,]),2),
                                round(mean(rfperf_gm12878_25kb_rus[19,]),2),
                                round(mean(rfperf_gm12878_25kb_rus[16,]),2),
                                round(mean(rfperf_gm12878_25kb_rus[15,]),2),
                                round(mean(rfperf_K562_25kb_rus[9,]),2),
                                round(mean(rfperf_K562_25kb_rus[19,]),2),
                                round(mean(rfperf_K562_25kb_rus[16,]),2),
                                round(mean(rfperf_K562_25kb_rus[15,]),2),
                                round(mean(rfperf_gm12878_25kb_ros[9,]),2),
                                round(mean(rfperf_gm12878_25kb_ros[19,]),2),
                                round(mean(rfperf_gm12878_25kb_ros[16,]),2),
                                round(mean(rfperf_gm12878_25kb_ros[15,]),2),
                                round(mean(rfperf_K562_25kb_ros[9,]),2),
                                round(mean(rfperf_K562_25kb_ros[19,]),2),
                                round(mean(rfperf_K562_25kb_ros[16,]),2),
                                round(mean(rfperf_K562_25kb_ros[15,]),2),
                                round(mean(rfperf_gm12878_25kb_smote[9,]),2),
                                round(mean(rfperf_gm12878_25kb_smote[19,]),2),
                                round(mean(rfperf_gm12878_25kb_smote[16,]),2),
                                round(mean(rfperf_gm12878_25kb_smote[15,]),2),
                                round(mean(rfperf_K562_25kb_smote[9,]),2),
                                round(mean(rfperf_K562_25kb_smote[19,]),2),
                                round(mean(rfperf_K562_25kb_smote[16,]),2),
                                round(mean(rfperf_K562_25kb_smote[15,]),2),
                                round(mean(rfperf_gm12878_25kb_rose[9,]),2),
                                round(mean(rfperf_gm12878_25kb_rose[19,]),2),
                                round(mean(rfperf_gm12878_25kb_rose[16,]),2),
                                round(mean(rfperf_gm12878_25kb_rose[15,]),2),
                                round(mean(rfperf_K562_25kb_rose[9,]),2),
                                round(mean(rfperf_K562_25kb_rose[19,]),2),
                                round(mean(rfperf_K562_25kb_rose[16,]),2),
                                round(mean(rfperf_K562_25kb_rose[15,]),2))

@@

f1mcc25kbplot <- ggplot(all25kbresults[which(all25kbresults$Metric=="F1-Score" |
                                               all25kbresults$Metric=="MCC"),],
                       aes(x=Resampling, y=Performance, fill=CL)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Cell Line")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

@@

all50kbresults$Performance <- c(round(rfperf_gm12878_50kb_none[9,2],2),
                                round(rfperf_gm12878_50kb_none[19,2],2),
                                round(rfperf_gm12878_50kb_none[16,2],2),
                                round(rfperf_gm12878_50kb_none[15,2],2),
                                round(rfperf_K562_50kb_none[9,2],2),
                                round(rfperf_K562_50kb_none[19,2],2),
                                round(rfperf_K562_50kb_none[16,2],2),
                                round(rfperf_K562_50kb_none[15,2],2),
                                round(mean(rfperf_gm12878_50kb_rus[9,]),2),
                                round(mean(rfperf_gm12878_50kb_rus[19,]),2),
                                round(mean(rfperf_gm12878_50kb_rus[16,]),2),
                                round(mean(rfperf_gm12878_50kb_rus[15,]),2),
                                round(mean(rfperf_K562_50kb_rus[9,]),2),
                                round(mean(rfperf_K562_50kb_rus[19,]),2),
                                round(mean(rfperf_K562_50kb_rus[16,]),2),
                                round(mean(rfperf_K562_50kb_rus[15,]),2),
                                round(mean(rfperf_gm12878_50kb_ros[9,]),2),
                                round(mean(rfperf_gm12878_50kb_ros[19,]),2),
                                round(mean(rfperf_gm12878_50kb_ros[16,]),2),
                                round(mean(rfperf_gm12878_50kb_ros[15,]),2),
                                round(mean(rfperf_K562_50kb_ros[9,]),2),
                                round(mean(rfperf_K562_50kb_ros[19,]),2),
                                round(mean(rfperf_K562_50kb_ros[16,]),2),
                                round(mean(rfperf_K562_50kb_ros[15,]),2),
                                round(mean(rfperf_gm12878_50kb_smote[9,]),2),
                                round(mean(rfperf_gm12878_50kb_smote[19,]),2),
                                round(mean(rfperf_gm12878_50kb_smote[16,]),2),
                                round(mean(rfperf_gm12878_50kb_smote[15,]),2),
                                round(mean(rfperf_K562_50kb_smote[9,]),2),
                                round(mean(rfperf_K562_50kb_smote[19,]),2),
                                round(mean(rfperf_K562_50kb_smote[16,]),2),
                                round(mean(rfperf_K562_50kb_smote[15,]),2),
                                round(mean(rfperf_gm12878_50kb_rose[9,]),2),
                                round(mean(rfperf_gm12878_50kb_rose[19,]),2),
                                round(mean(rfperf_gm12878_50kb_rose[16,]),2),
                                round(mean(rfperf_gm12878_50kb_rose[15,]),2),
                                round(mean(rfperf_K562_50kb_rose[9,]),2),
                                round(mean(rfperf_K562_50kb_rose[19,]),2),
                                round(mean(rfperf_K562_50kb_rose[16,]),2),
                                round(mean(rfperf_K562_50kb_rose[15,]),2))

@@

f1mcc50kbplot <- ggplot(all50kbresults[which(all50kbresults$Metric=="F1-Score" |
                                               all50kbresults$Metric=="MCC"),],
                       aes(x=Resampling, y=Performance, fill=CL)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Cell Line")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

@@

all100kbresults$Performance <- c(round(rfperf_gm12878_100kb_none[9,2],2),
                                round(rfperf_gm12878_100kb_none[19,2],2),
                                round(rfperf_gm12878_100kb_none[16,2],2),
                                round(rfperf_gm12878_100kb_none[15,2],2),
                                round(rfperf_K562_100kb_none[9,2],2),
                                round(rfperf_K562_100kb_none[19,2],2),
                                round(rfperf_K562_100kb_none[16,2],2),
                                round(rfperf_K562_100kb_none[15,2],2),
                                round(mean(rfperf_gm12878_100kb_rus[9,]),2),
                                round(mean(rfperf_gm12878_100kb_rus[19,]),2),
                                round(mean(rfperf_gm12878_100kb_rus[16,]),2),
                                round(mean(rfperf_gm12878_100kb_rus[15,]),2),
                                round(mean(rfperf_K562_100kb_rus[9,]),2),
                                round(mean(rfperf_K562_100kb_rus[19,]),2),
                                round(mean(rfperf_K562_100kb_rus[16,]),2),
                                round(mean(rfperf_K562_100kb_rus[15,]),2),
                                round(mean(rfperf_gm12878_100kb_ros[9,]),2),
                                round(mean(rfperf_gm12878_100kb_ros[19,]),2),
                                round(mean(rfperf_gm12878_100kb_ros[16,]),2),
                                round(mean(rfperf_gm12878_100kb_ros[15,]),2),
                                round(mean(rfperf_K562_100kb_ros[9,]),2),
                                round(mean(rfperf_K562_100kb_ros[19,]),2),
                                round(mean(rfperf_K562_100kb_ros[16,]),2),
                                round(mean(rfperf_K562_100kb_ros[15,]),2),
                                round(mean(rfperf_gm12878_100kb_smote[9,]),2),
                                round(mean(rfperf_gm12878_100kb_smote[19,]),2),
                                round(mean(rfperf_gm12878_100kb_smote[16,]),2),
                                round(mean(rfperf_gm12878_100kb_smote[15,]),2),
                                round(mean(rfperf_K562_100kb_smote[9,]),2),
                                round(mean(rfperf_K562_100kb_smote[19,]),2),
                                round(mean(rfperf_K562_100kb_smote[16,]),2),
                                round(mean(rfperf_K562_100kb_smote[15,]),2),
                                round(mean(rfperf_gm12878_100kb_rose[9,]),2),
                                round(mean(rfperf_gm12878_100kb_rose[19,]),2),
                                round(mean(rfperf_gm12878_100kb_rose[16,]),2),
                                round(mean(rfperf_gm12878_100kb_rose[15,]),2),
                                round(mean(rfperf_K562_100kb_rose[9,]),2),
                                round(mean(rfperf_K562_100kb_rose[19,]),2),
                                round(mean(rfperf_K562_100kb_rose[16,]),2),
                                round(mean(rfperf_K562_100kb_rose[15,]),2))

@@

f1mcc100kbplot <- ggplot(all100kbresults[which(all100kbresults$Metric=="F1-Score" |
                                               all100kbresults$Metric=="MCC"),],
                       aes(x=Resampling, y=Performance, fill=CL)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Cell Line")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

@@

#Table of model performances

@@

performancetab <- data.frame(Performance = c(rep("F1-Score", 10),
                                             rep("MCC", 10)),
                             Resampling = rep(c("None",
                                                "None",
                                                "RUS",
                                                "RUS",
                                                "ROS",
                                                "ROS",
                                                "SMOTE",
                                                "SMOTE",
                                                "ROSE",
                                                "ROSE"),2),
                             CL = rep(c("GM12878", "K562"), 10)
                             )

performancetab$kb10 <- c(rfperf_gm12878_10kb_none[16,2],
                         rfperf_K562_10kb_none[16,2],
                         mean(rfperf_gm12878_10kb_rus[16,]),
                         mean(rfperf_K562_10kb_rus[16,]),
                         mean(rfperf_gm12878_10kb_ros[16,]),
                         mean(rfperf_K562_10kb_ros[16,]),
                         mean(rfperf_gm12878_10kb_smote[16,]),
                         mean(rfperf_K562_10kb_smote[16,]),
                         mean(rfperf_gm12878_10kb_rose[16,]),
                         mean(rfperf_K562_10kb_rose[16,]),
                         rfperf_gm12878_10kb_none[15,2],
                         rfperf_K562_10kb_none[15,2],
                         mean(rfperf_gm12878_10kb_rus[15,]),
                         mean(rfperf_K562_10kb_rus[15,]),
                         mean(rfperf_gm12878_10kb_ros[15,]),
                         mean(rfperf_K562_10kb_ros[15,]),
                         mean(rfperf_gm12878_10kb_smote[15,]),
                         mean(rfperf_K562_10kb_smote[15,]),
                         mean(rfperf_gm12878_10kb_rose[15,]),
                         mean(rfperf_K562_10kb_rose[15,]))

performancetab$kb25 <- c(rfperf_gm12878_25kb_none[16,2],
                         rfperf_K562_25kb_none[16,2],
                         mean(rfperf_gm12878_25kb_rus[16,]),
                         mean(rfperf_K562_25kb_rus[16,]),
                         mean(rfperf_gm12878_25kb_ros[16,]),
                         mean(rfperf_K562_25kb_ros[16,]),
                         mean(rfperf_gm12878_25kb_smote[16,]),
                         mean(rfperf_K562_25kb_smote[16,]),
                         mean(rfperf_gm12878_25kb_rose[16,]),
                         mean(rfperf_K562_25kb_rose[16,]),
                         rfperf_gm12878_25kb_none[15,2],
                         rfperf_K562_25kb_none[15,2],
                         mean(rfperf_gm12878_25kb_rus[15,]),
                         mean(rfperf_K562_25kb_rus[15,]),
                         mean(rfperf_gm12878_25kb_ros[15,]),
                         mean(rfperf_K562_25kb_ros[15,]),
                         mean(rfperf_gm12878_25kb_smote[15,]),
                         mean(rfperf_K562_25kb_smote[15,]),
                         mean(rfperf_gm12878_25kb_rose[15,]),
                         mean(rfperf_K562_25kb_rose[15,]))

performancetab$kb50 <- c(rfperf_gm12878_50kb_none[16,2],
                         rfperf_K562_50kb_none[16,2],
                         mean(rfperf_gm12878_50kb_rus[16,]),
                         mean(rfperf_K562_50kb_rus[16,]),
                         mean(rfperf_gm12878_50kb_ros[16,]),
                         mean(rfperf_K562_50kb_ros[16,]),
                         mean(rfperf_gm12878_50kb_smote[16,]),
                         mean(rfperf_K562_50kb_smote[16,]),
                         mean(rfperf_gm12878_50kb_rose[16,]),
                         mean(rfperf_K562_50kb_rose[16,]),
                         rfperf_gm12878_50kb_none[15,2],
                         rfperf_K562_50kb_none[15,2],
                         mean(rfperf_gm12878_50kb_rus[15,]),
                         mean(rfperf_K562_50kb_rus[15,]),
                         mean(rfperf_gm12878_50kb_ros[15,]),
                         mean(rfperf_K562_50kb_ros[15,]),
                         mean(rfperf_gm12878_50kb_smote[15,]),
                         mean(rfperf_K562_50kb_smote[15,]),
                         mean(rfperf_gm12878_50kb_rose[15,]),
                         mean(rfperf_K562_50kb_rose[15,]))

performancetab$kb100 <- c(rfperf_gm12878_100kb_none[16,2],
                         rfperf_K562_100kb_none[16,2],
                         mean(rfperf_gm12878_100kb_rus[16,]),
                         mean(rfperf_K562_100kb_rus[16,]),
                         mean(rfperf_gm12878_100kb_ros[16,]),
                         mean(rfperf_K562_100kb_ros[16,]),
                         mean(rfperf_gm12878_100kb_smote[16,]),
                         mean(rfperf_K562_100kb_smote[16,]),
                         mean(rfperf_gm12878_100kb_rose[16,]),
                         mean(rfperf_K562_100kb_rose[16,]),
                         rfperf_gm12878_100kb_none[15,2],
                         rfperf_K562_100kb_none[15,2],
                         mean(rfperf_gm12878_100kb_rus[15,]),
                         mean(rfperf_K562_100kb_rus[15,]),
                         mean(rfperf_gm12878_100kb_ros[15,]),
                         mean(rfperf_K562_100kb_ros[15,]),
                         mean(rfperf_gm12878_100kb_smote[15,]),
                         mean(rfperf_K562_100kb_smote[15,]),
                         mean(rfperf_gm12878_100kb_rose[15,]),
                         mean(rfperf_K562_100kb_rose[15,]))

performancetab[,4:7] <- round(performancetab[,4:7], 3)
```
